Visualization and analysis of probability distributions of large temporal data

### 2021-11-05 Rmd/02-gravitas.Rmd
index and gitignore files update
sometimes I do rock, Don't I? successful thesis compilation

The purpose is to visualize the distribution of the continuous variable ($v$) conditional on the values of two granularities, $C_i$ and $C_j$. Since $C_i$ and $C_j$ are factors or categorical variables, data subsets corresponding to each combination of their levels form a subgroup and the visualization amounts to having displays of distributions for different subgroups. The response variable $(v)$ is plotted on the y-axis and the levels of $C_i (C_j)$ on the x-axis, conditional on the levels of $C_j (C_i)$. This means, carrying out the same plot corresponding to each level of the conditioning variable. This is consistent with the widely used grammar of graphics
which is a framework to construct statistical graphics by relating the data space to the graphic space [@Wilkinson1999-nk, @Wickham2009pk].

@@

The Australian authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research. Thanks to [Data61 CSIRO](https://data61.csiro.au/) for partially funding Sayani's research and Dr Peter Toscas for providing useful inputs on improving the analysis of the smart meter application. We would also like to thank Nicholas Spyrison for many useful discussions, sketching figures and feedback on the manuscript. The package `gravitas` was built during the [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). More details about the package can be found at [sayani07.github.io/gravitas](https://sayani07.github.io/gravitas/). The Github repository,  [github.com/Sayani07/paper-gravitas](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials. This article was created with `knitr` [@knitr, @R-knitr] and `rmarkdown` [@rmarkdown, @R-rmarkdown].

>>>>

The purpose is to visualize the distribution of the continuous variable ($v$) conditional on the values of two granularities, $C_i$ and $C_j$. Since $C_i$ and $C_j$ are factors or categorical variables, data subsets corresponding to each combination of their levels form a subgroup and the visualization amounts to having displays of distributions for different subgroups. The response variable $(v)$ is plotted on the y-axis and the levels of $C_i (C_j)$ on the x-axis, conditional on the levels of $C_j (C_i)$. This means, carrying out the same plot corresponding to each level of the conditioning variable. This is consistent with the widely used grammar of graphics
which is a framework to construct statistical graphics by relating the data space to the graphic space [@Wilkinson1999-nk], [@Wickham2009pk].

@@

The Australian authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research. Thanks to [Data61 CSIRO](https://data61.csiro.au/) for partially funding Sayani's research and Dr Peter Toscas for providing useful inputs on improving the analysis of the smart meter application. We would also like to thank Nicholas Spyrison for many useful discussions, sketching figures and feedback on the manuscript. The package `gravitas` was built during the [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). More details about the package can be found at [sayani07.github.io/gravitas](https://sayani07.github.io/gravitas/). The Github repository,  [github.com/Sayani07/paper-gravitas](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials. This article was created with `knitr` [@knitr], [@R-knitr] and `rmarkdown` [@rmarkdown], [@R-rmarkdown].

### 2021-11-05 Rmd/03-hakear.Rmd
sometimes I do rock, Don't I? successful thesis compilation

Cyclic temporal granularities [@Bettini1998-ed, @Gupta2021-hd] are <!--theoretical--> temporal deconstructions that define cyclic repetitions in time, e.g. hour-of-day, day-of-month, or regularly scheduled public holidays. These granularities form ordered or unordered categorical variables. An example of an ordered granularity is day-of-week, where Tuesday is always followed by Wednesday, and so on. An unordered granularity example is different week types in a semester, orientation, break, exam or regular classes in an academic calendar. Using granularities to  explore patterns in univariate time series can be considered to be examining the distribution of the measured variable across different categories of the cyclic granularities.

@@

The Australian authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research. Sayani Gupta was partially funded by [Data61 CSIRO](https://data61.csiro.au/) during her PhD. The Github repository,  [github.com/Sayani07/paper-hakear](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials. This article was created with R [@R-language], `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown]. Graphics are produced with @Wickham2009pk.

>>>>

Cyclic temporal granularities [@Bettini1998-ed], [@Gupta2021-hd] are <!--theoretical--> temporal deconstructions that define cyclic repetitions in time, e.g. hour-of-day, day-of-month, or regularly scheduled public holidays. These granularities form ordered or unordered categorical variables. An example of an ordered granularity is day-of-week, where Tuesday is always followed by Wednesday, and so on. An unordered granularity example is different week types in a semester, orientation, break, exam or regular classes in an academic calendar. Using granularities to  explore patterns in univariate time series can be considered to be examining the distribution of the measured variable across different categories of the cyclic granularities.

@@

The Australian authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research. Sayani Gupta was partially funded by [Data61 CSIRO](https://data61.csiro.au/) during her PhD. The Github repository,  [github.com/Sayani07/paper-hakear](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials. This article was created with R [@R-language], `knitr` [@knitr2015], [@R-knitr] and `rmarkdown` [@rmarkdown2018], [@R-rmarkdown]. Graphics are produced with @Wickham2009pk.

### 2021-11-05 index.Rmd
sometimes I do rock, Don't I? successful thesis compilation

---
title: "Visualization and analysis of probability distributions of large temporal data"
author: "Sayani Gupta"
degreetype: Doctor of Philosophy
site: bookdown::bookdown_site
degrees: M.Stat, B.Sc (Stat Hons)
bibliography:
- bib/gravitas.bib
- bib/hakear.bib
- bib/gracsr.bib
- bib/thesisrefs.bib
link-citations: yes
---

>>>>

---
title: "Visualization and analysis of probability distributions of large temporal data"
author: "Sayani Gupta"
degreetype: Doctor of Philosophy
site: bookdown::bookdown_site
degrees: M.Stat, B.Sc (Stat Hons)
bibliography: [bib/gravitas.bib, bib/hakear.bib, bib/gracsr.bib, bib/thesisrefs.bib]
link-citations: yes
---
